Schramm-Loewner evolution in tricritical Ising model

### 2013-07-24 AffineLieAlgebras/Simons/paper.tex

  We are interested in the case $A_4$, so we have
$2\cos\lambda=\frac{1+\sqrt{5}}{2}$, $\lambda=\pi/5$, $\psi=\left[1,2\cos\lambda,2\cos\lambda,1\right]$.
$2\cos\lambda=\frac{\sqrt{\sqrt{5}+3}}{\sqrt{2}}$,
$\lambda=0.62831853071796$ and $\psi=\left[1,2\cos\lambda,
  4\cos^2\lambda-1, 2cos\lambda-\frac{1}{2\cos\lambda}\right]$ or $\psi=\left[1,\frac{\sqrt{\sqrt{5}+3}}{\sqrt{2}},\frac{\sqrt{5}+1}{2},\frac{\sqrt{\sqrt{5}+3}\,\left( \sqrt{2}\,\sqrt{5}-\sqrt{2}\right) }{4}\right]$.

@@

@@

We consider the model on the domain with a boundary (upper half-plane). So we need to impose
conformally invariant boundary conditions.

>>>>

  We are interested in the case $A_4$, so we have

$2\cos\lambda=\frac{\sqrt{\sqrt{5}+3}}{\sqrt{2}}$,
$\lambda=0.62831853071796$ and $\psi=\left[1,2\cos\lambda,
  4\cos^2\lambda-1, 2cos\lambda-\frac{1}{2\cos\lambda}\right]$ or $\psi=\left[1,\frac{\sqrt{\sqrt{5}+3}}{\sqrt{2}},\frac{\sqrt{5}+1}{2},\frac{\sqrt{\sqrt{5}+3}\,\left( \sqrt{2}\,\sqrt{5}-\sqrt{2}\right) }{4}\right]$.
The isotropic case $u=\lambda/2$ with boundary parameters
$u=\xi_1=\xi_2=\lambda/2$ corresponds to the  conformal point. Then we have
$s_1(-u)=\frac{\sin\lambda/2}{\sin\lambda}=\frac{1}{2\cos\lambda/2}$ and $s_0(u)=\frac{1}{2\cos\lambda/2}$.

\begin{itemize}
\item Boltzmann weights for $A_{4}$
\item Boundary weights ?
\item Critical point, isotropicity

$2\cos\lambda=\frac{1+\sqrt{5}}{2}$, $\lambda=\pi/5$, $\psi=\left[1,2\cos\lambda,2\cos\lambda,1\right]$.
$2\cos\lambda=\frac{\sqrt{\sqrt{5}+3}}{\sqrt{2}}$,
$\lambda=0.62831853071796$ and $\psi=\left[1,2\cos\lambda,
  4\cos^2\lambda-1, 2cos\lambda-\frac{1}{2\cos\lambda}\right]$ or $\psi=\left[1,\frac{\sqrt{\sqrt{5}+3}}{\sqrt{2}},\frac{\sqrt{5}+1}{2},\frac{\sqrt{\sqrt{5}+3}\,\left( \sqrt{2}\,\sqrt{5}-\sqrt{2}\right) }{4}\right]$.

@@

In recent
years theoretical progress in the study of critical behavior was connected with the description of
geometrical objects -- interfaces. It was achieved by the use of Scharmm-Loewner evolution \cite{schramm2000scaling}.

The behaviour of the dilute Ising model in tricritical
point is described by conformal field theory (CFT) with central charge $c=\frac{7}{10}$
\cite{friedan1985superconformal}.

Shramm-Loewner evolution is the stochastic differential equation that describes the growth of
conformally-invariant cut

\begin{equation}
  \label{eq:6}

\end{equation}

We use CFT data to establish the value of Schramm-Loewner evolution parameter $\kappa$. The relation
$c=\frac{(8-3\kappa)(\kappa-6)}{2\kappa}$ gives us possible values of $\kappa=\frac{16}{5},\; 5$.

@@
